---
title: "Gender, Employment and Income"
author: "Ama Owusu-Darko"
format: html
editor: visual
---

## Topic

I am a graduate student in Ghana. My research is exploring the mediating effect of gender in the causal pathway of employment and income in the agricultural sector in 5 West African countries.

```{r packages}
#| echo: false
library(tidyverse)  # general use ----
library(here)       # file paths  ----
library(haven)      # import .sav files ----  
library(labelled)   # tools for labelled data ----
library(sjlabelled) # more tools for labelled data ----
```

```{r get_data}
#| echo: false

# Five data sets for 5 West African countries
library(haven)
gha21 <- read_stata("C:/Users/Korantema/Downloads/UNHCR_GHA_2021_LIS_data_v1_1.zip")

chd21 <- read_dta("C:/Users/Korantema/Downloads/UNHCR_LIS_data_v1_1/UNHCR_TCD_2021_LIS_data_v1.1.dta")
cmr21 <- read_dta("C:/Users/Korantema/Downloads/UNHCR_LIS_data_v1_1/UNHCR_CMR_2021_LIS_data_v1.1.dta")

nger21 <- read_dta("C:/Users/Korantema/Downloads/UNHCR_LIS_data_v1_1/UNHCR_NER_2021_LIS_data_v1.1.dta")

nga21 <- read_dta("C:/Users/Korantema/Downloads/UNHCR_LIS_data_v1_1/UNHCR_NGA_2021_LIS_data_v1.1.dta")



```

```{r dictionary}

# create data dictionary ----
gh_dictionary <- labelled::generate_dictionary(gha21)


```

#### Get data, load packages, ..... **combine data**

create my own id after combining

```{r na_columns}
#find  and remove na columns
gh_na<-gha21 |> purrr::keep(~!all(is.na(.)))
gh_names<- names(gh_na) #character vector
cmr_na<- cmr21 |> purrr::keep(~!all(is.na(.)))
cmr_names<- names(cmr_na)

nger_na <-nger21 |> purrr::keep(~!all(is.na(.)))
nga_na<- nga21|> purrr::keep(~!all(is.na(.)))

chd_na <- chd21 |> purrr::keep(~!all(is.na(.)))


intersect(gh_names,cmr_names)#, names(nger_na),names(chd_na),names(nga_na))

intersect(intersect(gh_names,cmr_names), intersect(names(nger_na),names(chd_na)))

inter_cols<-intersect(names(nga_na),(intersect(intersect(gh_names,cmr_names), intersect(names(nger_na),names(chd_na)))))
          
gha<-gha21 |> select(all_of(inter_cols))
dictionary <- labelled::generate_dictionary(gha)
#nger<- nger21 |> select(all_of(inter_cols))

#cmr<-cmr21 |> select(all_of(inter_cols))
#chd<-chd21 |> select(all_of(inter_cols))

#nga<- nga21 |> select(all_of(inter_cols))



```

```{r as_factor}


factor_out<- function(df){
  df |> select(all_of(inter_cols)) |> 
    #[,1:11]|> 
    #dplyr::select(c(31:30)) |>
    dplyr::mutate(across(c(STATUS,Country:BE, Gender:CountryOrigin, 
                           Education,MaritalStatus,O1SubSector:Crop1,
                           Crop2, Animal1, O1IncomeYear:O2EmployRegistered,
                           O2EmployOthers:O2EmploymentSector)
                           ,haven::as_factor)) #|>
    #dplyr::mutate(across(c(2,4:12,  16:18, 20:21,24:25),haven::as_factor)) |> 
   # summary()
}

#first_10(wa5)  
#wa5<-
#purrr::map(wa5|> dplyr::select(c(1:11)),first_10)

#wa5_list<-c(gha, chd, cmr,nger,nga)
#purrr::map(wa5_list,factor_out)
```

```{r wa5}
wa5_data<-dplyr::bind_rows(factor_out(gha21),factor_out(chd21),factor_out(cmr21),factor_out(nger21),factor_out(nga21))

library(arrow)

wa5_data |> 
  group_by(Country) |> 
  arrow::write_dataset("wa5", format="parquet")

str(wa5_data)

```

## Data Source

**Livelihoods Programme Monitoring Beneficiary Survey, 2021**

Unit of analysis- household

## Methodology

I downloaded the data sets for 5 West African countries, Ghana, Nigeria, Niger, Chad, Cameroon.

Links-

-   [Nigeria - Livelihoods Programme Monitoring Beneficiary Survey, 2021 (unhcr.org)](https://microdata.unhcr.org/index.php/catalog/756/get-microdata)

-   [Cameroon - Livelihoods Programme Monitoring Beneficiary Survey, 2021 (unhcr.org)](https://microdata.unhcr.org/index.php/catalog/745/get-microdata)


### Data Cleaning of dta files

All data sets have 104 variables (columns) but the categorical data has different labels.

## References

UNHCR (2021). Niger: Livelihoods Programme Monitoring Beneficiary Survey, 2021. Accessed from: [https://microdata.unhcr.org](https://microdata.unhcr.org/)


UNHCR (2021). Chad: Livelihoods Programme Monitoring Beneficiary Survey, 2021. Accessed from: [https://microdata.unhcr.org](https://microdata.unhcr.org/)

