---
title: "Gender, Employment and Income"
author: "Ama Owusu-Darko"
format: html
editor: visual
---

## Topic

I am a graduate student in Ghana. My research is exploring the mediating effect of gender in the causal pathway of employment and income in the agricultural sector in 5 West African countries.

```{r get_data}
#| echo: false

# Five data sets for 5 West African countries
library(haven)
gha21 <- read_stata("C:/Users/Korantema/Downloads/UNHCR_GHA_2021_LIS_data_v1_1.zip")



```

```{r add_country_code}

get_labels(gha21$Country)

```

## Data Source

**Livelihoods Programme Monitoring Beneficiary Survey, 2021**

Unit of analysis- household

## Methodology

I downloaded the data sets for 5 West African countries, Ghana, Nigeria, Niger, Chad, Cameroon.

Links-

-   [Nigeria - Livelihoods Programme Monitoring Beneficiary Survey, 2021 (unhcr.org)](https://microdata.unhcr.org/index.php/catalog/756/get-microdata)

-   [Cameroon - Livelihoods Programme Monitoring Beneficiary Survey, 2021 (unhcr.org)](https://microdata.unhcr.org/index.php/catalog/745/get-microdata)


### Data Cleaning of dta files

All data sets have 104 variables (columns) but the categorical data has different labels.

## References

UNHCR (2021). Niger: Livelihoods Programme Monitoring Beneficiary Survey, 2021. Accessed from: [https://microdata.unhcr.org](https://microdata.unhcr.org/)


UNHCR (2021). Chad: Livelihoods Programme Monitoring Beneficiary Survey, 2021. Accessed from: [https://microdata.unhcr.org](https://microdata.unhcr.org/)

